---
title: "Second Species Prediction"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

source("/home/canura26/ColbyForecasting/setup.R")
for (f in list.files("/home/canura26/ColbyForecasting/functions",
     pattern = glob2rx("*.R"), full.names = TRUE)){
  source(f)
}

SPECIES = "Galeocerdo cuvier"
```

```{r load_covar}
cfg = read_configuration(scientificname = SPECIES,
                         version = "v1", 
                         path = data_path("models"))
db = brickman_database()
db = brickman_database()
present_conditions = read_brickman(db |> filter(scenario == "PRESENT", 
                                                interval == "mon"),
                       add = c("depth", "month")) |>
  select(all_of(cfg$keep_vars))
```

```{r load_workflow}
model_fits = read_model_fit(filename = "Galeocerdo_cuvier-v1-model_fits")
model_fits
```

```{r nowcast}
nowcast = predict_stars(model_fits, present_conditions)
nowcast
```

```{r plot_nowcast_maxent, warning = FALSE}
plot_prediction(nowcast['default_btree'])
```

```{r plot_class_labels, warning = FALSE}
pa_nowcast = threshold_prediction(nowcast)
plot_prediction(pa_nowcast['default_btree'])
```

```{r load_2075_RCP85, warning = FALSE}
covars_rcp85_2075 = read_brickman(db |> filter(scenario == "RCP85", 
                                               year == 2075, 
                                               interval == "mon"),
                                  add = c("depth", "month")) |>
  mutate(depth = log10(depth)) |>
  select(all_of(cfg$keep_vars))
```

<<<<<<< HEAD
```{r load_2055_RCP85, warning = FALSE}
covars_rcp85_2055 = read_brickman(db |> filter(scenario == "RCP85", 
                                               year == 2055, 
                                               interval == "mon"),
                                  add = c("depth", "month")) |>
  mutate(depth = log10(depth)) |>
  select(all_of(cfg$keep_vars))
```

```{r load_2075_RCP45, warning = FALSE}
covars_rcp45_2075 = read_brickman(db |> filter(scenario == "RCP45", 
                                               year == 2075, 
                                               interval == "mon"),
                                  add = c("depth", "month")) |>
  mutate(depth = log10(depth)) |>
  select(all_of(cfg$keep_vars))
```

```{r load_2055_RCP45, warning = FALSE}
covars_rcp45_2055 = read_brickman(db |> filter(scenario == "RCP45", 
                                               year == 2055, 
                                               interval == "mon"),
                                  add = c("depth", "month")) |>
  mutate(depth = log10(depth)) |>
  select(all_of(cfg$keep_vars))
```

```{r forecast}
rcp85_2075 = predict_stars(model_fits, covars_rcp85_2075)

rcp85_2055 = predict_stars(model_fits, covars_rcp85_2055)

rcp45_2075 = predict_stars(model_fits, covars_rcp45_2075)

rcp45_2055 = predict_stars(model_fits, covars_rcp45_2055)
```

```{r plot_forecast, warning = FALSE}
plot_prediction(forecast_2075['default_btree'])
```

```{r save_pred}
# make sure the output directory exists
path = make_path("predictions")

write_prediction(nowcast,
                 scientificname = cfg$scientificname,
                 version = cfg$version,
                 year = "CURRENT",
                 scenario = "CURRENT")

write_prediction(rcp85_2075,
                 scientificname = cfg$scientificname,
                 version = cfg$version,
                 year = "2075",
                 scenario = "RCP85")

write_prediction(rcp85_2055,
                 scientificname = cfg$scientificname,
                 version = cfg$version,
                 year = "2055",
                 scenario = "RCP85")

write_prediction(rcp45_2075,
                 scientificname = cfg$scientificname,
                 version = cfg$version,
                 year = "2075",
                 scenario = "RCP45")

write_prediction(rcp45_2055,
                 scientificname = cfg$scientificname,
                 version = cfg$version,
                 year = "2055",
                 scenario = "RCP45")
```
